Risk Perceptions for Wearable Devices

### 2015-01-07 wearables_survey.tex
Added verbiage for risks/benefits

When assessing new technologies, participants generally rated all new technologies and new wearables similarly, considering them low risk and low benefit (see figure \ref{fig:techplot}). We suspect that these similar assessments are because most are not consciously aware of the possibilities of these technologies or how they are being used today.

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{techplot.png}
	\caption{(This is a placeholder! TODO: generate a better plot; take out the specific wearables too.)}
	\label{fig:techplot}
\end{figure}

Participants rated the the most familiar technologies as the most beneficial; 5 most beneficial technologies were internet, laptops, email, smartphones, and location tracking. Again, we believe this is the result of exposure people have to these technologies--most people are exposed to these devices and use location-based applications. The most risky technologies were ones perceived to be privacy-invasive; 5 most risky technologies were facial recognition, internet, discreet video camera, location tracking, and facial detection. People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a physical lawnmower. It is fair to say that, these assessments of the most risky or beneficial technologies may not be the most accurate, but do reflect the exposure of various technologies to the general public and also prove that people do perceive risks in a real way related to these technologies.

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=0.47\textwidth]{riskbenefit.pdf}
	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
	\label{fig:techplot}
\end{figure}

We asked participants to rate new capabilities related to wearable technologies (e.g., facial recognition) in terms of their risks and benefits. We also asked them to do this for technologies with which they were likely to be more familiar (e.g., smartphones and laptops) in addition to two examples of specific wearable devices, Google Glass and the fictitious Cubetastic3000. They did this alongside well-establish technologies studied by Fischhoff\etal\cite{Fischhoff}, which we used to calibrate our results. When assessing new technologies, participants generally rated all familiar technologies and those related to wearables as being low-risk. Figure \ref{fig:techplot} depicts participants' median ratings. We found that the calibration technologies were all rated as the most risky. At the same time, with the exception of electricity, the calibration technologies were seen as lower benefit than the others.

As a group, participants rated the familiar technologies as the most beneficial. We believe this is the result of exposure people have to these technologies---most people use these technologies daily. Of the wearable technologies, the most risky were ones perceived to be privacy-invasive; the most risky technologies were facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal---albeit equivalent---risk levels (i.e., a median of ``10''). People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a lawnmower.

At the same time, these perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits, but they do reflect the general public's present exposure to these technologies and also show that people do perceive specific risks and benefits. We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used. We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).
